---
title: "Inter-agent calibration and cellular gonad homogeneity : *Mullus surmuletus*"
df_print: kable
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

# Introduction

Data on the stereological readings of the the red-mullet (Mullus surmuletus). 
For the inter-agent calibration, four agents read the same 15 histological slides. The goal of this exercise was to show the differences between readings from different operators (percentage agreement) with different degrees of knowledge on histological ovarian structures. 
For the cellular homogeneity check, both ovaries of 15 fish were sectioned in the anterior, posterior and median positions. Cellular counts were analysed and compared.


```{r , message=FALSE, warning=FALSE}
library(BiocManager)
library(RBioFormats)
library(rJava)
library(EBImage)
library(xml2)
library(magick)
library(RColorBrewer)
library("dplyr")
library(ggplot2)
library(irr)
library(tidyr)
library(readxl)
library(gt)
```

# Inter-agent calibration

Uploading the First Reading data from all agents.

## I - Visual results comparison

Visual projection of the reading results for four readers (ALM, VM, CS), for one slide (MULL_SUR_139_G).

```{r data 1, results='hide', fig.height=10, fig.width=10}

setwd('C:/Users/csauger/Documents/These/Analyses/rouget_barbet')

# path to vsi and xml files
fileimg<- c('C:/Users/csauger/Documents/These/Images_poissons/rouget_barbet/Scans/MULL_SUR_139_G.vsi')
L2xmlALM<- c('C:/Users/csauger/Documents/These/Data/rouget/Lectures/Calibration/L2/ALM/MULL_SUR_139_G.vsi_.xml')
L2xmlVM<- c('C:/Users/csauger/Documents/These/Data/rouget/Lectures/Calibration/L2/VM/MULL_SUR_139_G.vsi_.xml')
L2xmlCS<- c('C:/Users/csauger/Documents/These/Data/rouget/Lectures/Calibration/L2/CS/MULL_SUR_139_G.vsi_.xml')

```

```{r plot1, results='hide', fig.height=10, fig.width=10}

metadata<-read.metadata(fileimg)
metadata

# Process the metadata of the scanned slide (to have the image ratio vs reading coordinates)
m <- do.call(rbind, lapply(coreMetadata(metadata),data.frame))

#info on the image with max size in sizeX (aka the spatial reference of the slides reading)
maxdim<-m[which.max(m$sizeX),]

#selection of an image with a tractable size for R (and the computer)
#here we used the series 3 with the resolution 6
IDseries<-3;IDres<-6

#dimension of the selected image (aka the spatial reference of the selected image)
actualdim<-m[m$series==IDseries&m$resolutionLevel==IDres,]

#compute the conversion factor between the reading coordinates and the selected image
fx<-actualdim$sizeX/maxdim$sizeX
fy<-actualdim$sizeY/maxdim$sizeY

# read the vsi image and plot it !
img0<- read.image(fileimg,series=IDseries,resolution=IDres,normalize=T)
plot(img0)
```

Plot 2 : Plot of the histological slide scanned with the reading results of agents ALM, VM and CS.

```{r , fig.height=10,fig.width=10}
# A function to read xml information
readinfoxml<-function(nomfich){
	xmlraw<-read_xml(nomfich)
  	nomnode<-xml_attr(xml_children(xmlraw),"Name")
  	whichtypecell<-which(nomnode%in%c('og','po1','po2','ldo','cao','vtg','oih','ho','POF','aoA','aoB','L','gw','ct','bv','Is','U','E'))
  	rez<-data.frame()
	for(i in whichtypecell){
	  typecell<-xml_attr(xml_children(xmlraw)[[i]],"Name")
	  locpt<- xml_find_all(xml_children(xml_children(xmlraw)[[i]]),"Region")
	  if(length(locpt)>0){
		  xytmp<-data.frame()
		  for(j in 1:length(locpt)){
			  vertex<-xml_children(xml_children(locpt[[j]]))
			  xtmp<-mean(as.numeric(xml_attr(vertex,"X")))
			  ytmp<-mean(as.numeric(xml_attr(vertex,"Y")))
			  xytmp<-rbind(xytmp,data.frame(idpt=j,x=xtmp,y=ytmp))
	  	}
	  rez<-rbind(rez,data.frame(typecell=typecell,idpt=xytmp$idpt,x=xytmp$x,y=xytmp$y))
	}
  	}
	return(rez)
}

# apply the function to the slide read above
infoALM<-readinfoxml(L2xmlALM)
infoVM<-readinfoxml(L2xmlVM)
infoCS<-readinfoxml(L2xmlCS)

```

Plot the reading results of the agents (ALM red, VM blue, CS purple) over the slide picture

```{r plot2, results='hide', fig.height=10, fig.width=10}

# plot and show 
plot(img0)
points(fx*infoALM$x,infoVM$y*fy,pch=".")
text(fx*infoVM$x,infoVM$y*fy,label=infoVM$typecell, col="blue")
text(fx*infoALM$x,infoALM$y*fy,label=infoALM$typecell, col="red")
text(fx*infoCS$x,infoCS$y*fy,label=infoCS$typecell, col="purple")

```

A id column is added, generated by combining the x and y coordinates to obtain an unique name for each sampled point of the reading grid. This will also help in checking if all readers have the same stereology grid.

```{r data2, results='hide'}

tmp <- dplyr::bind_rows(list(ALM=infoALM, VM=infoVM, CS=infoCS), .id = 'agent')
tmp1 <- tmp  %>%   unite("id", x:y, remove = FALSE) 
tmp1 <- tmp1 %>% group_by(id) %>% mutate(nbtype=n_distinct(typecell))%>%ungroup()

```

Plot 3 : Plot of the histological slide scanned with the reading results that differ between agents ALM, VM and CS.

```{r plot3, fig.height=10,fig.width=10}

plot(img0)
listreader<-unique(tmp1$agent)
nbreader<-length(listreader)
couleur<-brewer.pal(nbreader,"Set3")
ylag<-c(-50,0,50)
xlag<-rep(-50,nbreader)
xyko<-tmp1%>%filter(nbtype!=1)
points(tmp1$x*fx,tmp1$y*fy,pch=20,col="black",cex=.5)#black points
legend("topright",legend=listreader,col=couleur,inset=.01,pch=20)
for(j in 1:nbreader){
    tmp2<-xyko%>%filter(agent==listreader[j])
    text(tmp2$x*fx,tmp2$y*fy,label=tmp2$typecell,col=couleur[j],pos=NULL,cex=.9)
}

```

## II - First Reading

Set up the data list to get for the first reading 

```{r data3, results='hide'}
pathdata <-"C:/Users/csauger/Documents/These/Data/rouget/Lectures/Calibration/L1"
list1<-dir(paste0(pathdata,"/ALM"),patt="xml",full=T)
list2<-dir(paste0(pathdata,"/VM"),patt="xml",full=T)
list4<-dir(paste0(pathdata,"/CS"),patt="xml",full=T)
listcal<-c(list1,list2,list4)

```

Uploading the First Reading data from all 2 agents.

**readposition** is a function that will allow us to read the .xml files containing the stereology reading results of the agents, and extract information such as the agent that did the reading, the slide’s name ID, the structure’s name and their x and y coordonates. A loop is set up to import the .xml information, extracted with the readposition function, into a dataframe rezall.

```{r data4, results='hide'}

readposition<-function(nomfich){
xmlraw<-read_xml(listcal[idnom])
  nomnode<-xml_attr(xml_children(xmlraw),"Name")
  whichtypecell<-which(nomnode%in%c("og","po1","po2","cao","vtg","oih","ho","POF","aoA","aoB","L","gw","ct","bv","Is","U","E"))
  rez<-data.frame()
  for(i in whichtypecell){
      typecell<-xml_attr(xml_children(xmlraw)[[i]],"Name")
      locpt<- xml_find_all(xml_children(xml_children(xmlraw)[[i]]),"Region")
      if(length(locpt)>0){
      xytmp<-data.frame()
      for(j in 1:length(locpt)){
          vertex<-xml_children(xml_children(locpt[[j]]))
          xtmp<-as.numeric(xml_attr(vertex,"X"))
          ytmp<-as.numeric(xml_attr(vertex,"Y"))
          xytmp<-rbind(xytmp,data.frame(idpt=j,x=xtmp,y=ytmp))
      }
      rez<-rbind(rez,data.frame(typecell=typecell,idpt=xytmp$idpt,x=xytmp$x,y=xytmp$y))
      }
  }
    rez<-rez%>%group_by(typecell,idpt)%>%summarise_all(median)%>%ungroup()%>%mutate(lame=listcal[idnom])
    agent<-sapply(strsplit(rez$lame,"/"),tail,2)
    rez$agent<-agent[1,]
    rez$slideid<-gsub(".xml","",agent[2,])
    rez<- rez%>%mutate(slideid=substr(slideid,1, nchar(slideid)-5))
    rez<-rez%>%select(-lame)
    return(rez)
}
rezallL1<-data.frame()
for(idnom in 1:length(listcal)){
  print(paste(idnom,listcal[idnom]))
  rez <- readposition(listcal[idnom])
  rez<-rez%>%group_by(slideid,x, y)%>%ungroup()
  rezallL1<-rbind(rez,rezallL1)
}

```
Checking if every agent has the same number of sampling points read

```{r , message=FALSE}
countcheck <- rezallL1 %>% group_by(slideid, agent) %>% summarise(total_points= n())
countcheck <- countcheck %>% spread(key = "agent", value = total_points)
countcheck
```

Set up of the main dataframe
We add the same color codes (colormat), used during the stereology reading, to the reading results dataframe (tmp).

```{r , results='hide'}
tmp <- rezallL1 %>% unite("id", x:y, remove = FALSE)
tmp <- tmp %>% mutate(reading = "1")
colormat<-data.frame(typecell= c("og","po1","po2","cao","vtg","oih","ho","POF","aoA","aoB","L","gw","ct","bv","Is","U","E"), matcolor =  c("lightgoldenrod1","yellow","orange","gray0","lightpink1","deeppink2","darkslategray1","cyan3","gray52","gray88","thistle1","darkgreen","seagreen1","firebrick1","cornflowerblue","mediumpurple3","white"), stringsAsFactors = F)
tmp <-left_join(tmp,colormat,by="typecell")
```

We re-organize the dataframe, adding the total number of points counted for each slide (total_points), the agent that did the reading, the name of the slide (slideid) and the percentage count of each structure (fract_estim).

The 17 cellular structures that can be found are :

-**og**: oogonium  
-**po1**: primary oocyte stage 1  
-**po2**: primary oocyte stage 2 
-**cao**: cortical alveoli oocyte  
-**vtg**: oocyte in vitellogenesis  
-**oih**: oocyte in hydration  
-**oh**: hydrated oocyte  
-**POF**: post-Ovulatory Follicle  
-**aoA**: atretic oocyte alpha  
-**aoB**: atretic oocyte beta  
-**L**: lysis  
-**bv**: blood vessel  
-**Is**: intercellular space  
-**gw**: gonadal wall  
-**ct**: connective tissue  
-**E**: unatural emptiness  
-**U**: undetermined 


```{r , results='hide',message=FALSE}
histo2 <- rezallL1 %>% group_by(typecell, slideid, agent) %>% summarise(hit_points= n())
histo3 <- histo2 %>% spread(key = "typecell", value = hit_points) 
histo3[is.na(histo3)] <- 0
histo4 <- (histo3[,3:19]*100)/(rowSums(histo3[,3:19]))#check number of columns histo3
histo5 <- cbind(histo4, histo3$slideid) %>% rename(slideid = `histo3$slideid`)
histo6 <- rezallL1 %>% group_by(slideid, agent) %>% summarise(total_points= n())
histo5 <- cbind(histo5, histo6$total_points) %>% rename(total_points = `histo6$total_points`)
histo5 <- cbind(histo5, histo6$agent) %>% rename(agent = `histo6$agent`)

stereoL1 <- gather(histo5, key = "typecell", value = fract_estim, aoA,aoB,bv,cao,ct,E,gw,ho,Is,L,og,oih,po1,po2,POF,U,vtg)

```

Plot 4: Results of the first reading exercise, for 15 slides by 2 agents

```{r plot4, fig.height=10,fig.width=15}
hist_tot_dif <- ggplot(data=stereoL1, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent : ")
hist_tot_dif
#ggsave(hist_tot_dif, file = "C:/Users/vmartin/Desktop/Stage/pour_erreur/hist_tot_dif.png")
```

Comparing the reading results for all 15 slides

Statistics on the counted surface values found by 4 readers

-minsurf % : minimum value, for the counted cellular structure (%), found between the 3 reading agents  
-maxsurf % : maximum value, for the counted cellular structure (%), found between the 3 reading agents  
-diffperc % : diffrence between the min (minsurf) and the max (maxsurf) values  
-sdperc % : standard deviation for the min and max values found between the reading agents  
-meanperc % : mean of the min and max values found between the reading agents  
-CV % : Coefficient of Variation, no unit, expressed in %.  
-medianeperc % : median value (%) of the counted cellular structures  
-madperc % : Mean Absolute Deviation of the counted cellular structures (%).  

### **1 - Slide MULL_SUR_072_D**

```{r plot5}
stereoL1_72D <- stereoL1 %>% filter(slideid == "MULL_SUR_072_D")

ggplot(data=stereoL1_72D, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_72D <- stereoL1_72D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test72D<-stereoL1_72D #%>% filter(diffperc > 3)
gt(test72D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  )

Diff_72D <- as.data.frame(test72D$diffperc)
```

```{r}
tmpstereoL1_72D <- tmp %>% filter(slideid=="MULL_SUR_072_D")
tmpstereoL1_72D <-tmpstereoL1_72D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_72D <-tidyr::spread(tmpstereoL1_72D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_72D)
```

```{r}
kappam.fleiss(tmpstereoL1_72D)
```

### **2 - MULL_SUR_091_G**

```{r plot6}
stereoL1_91G <- stereoL1 %>% filter(slideid == "MULL_SUR_091_G")

ggplot(data=stereoL1_91G, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_91G <- stereoL1_91G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test91G<-stereoL1_91G #%>% filter(diffperc > 3)
gt(test91G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 
Diff_91G <- as.data.frame(test91G$diffperc)
```


```{r}
tmpstereoL1_91G  <- tmp %>% filter(slideid=="MULL_SUR_091_G")
tmpstereoL1_91G  <-tmpstereoL1_91G %>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_91G  <-tidyr::spread(tmpstereoL1_91G ,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_91G )
```

```{r}
kappam.fleiss(tmpstereoL1_91G)
```

### **3 - Slide MULL_SUR_096_D**

```{r plot7}
stereoL1_96D <- stereoL1 %>% filter(slideid == "MULL_SUR_096_D")

ggplot(data=stereoL1_96D, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_96D <- stereoL1_96D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test96D<-stereoL1_96D #%>% filter(diffperc > 3)
gt(test96D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_96D <- as.data.frame(test96D$diffperc)
```


```{r}
tmpstereoL1_96D <- tmp %>% filter(slideid=="MULL_SUR_096_D")
tmpstereoL1_96D <-tmpstereoL1_96D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_96D <-tidyr::spread(tmpstereoL1_96D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_96D)
```

```{r}
kappam.fleiss(tmpstereoL1_96D)
```


### **4 - Slide MULL_SUR_097_D**

```{r plot8}
stereoL1_97D <- stereoL1 %>% filter(slideid == "MULL_SUR_097_D")

ggplot(data=stereoL1_97D, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_97D <- stereoL1_97D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test97D<-stereoL1_97D #%>% filter(diffperc > 3)
gt(test97D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_97D <- as.data.frame(test97D$diffperc)
```


```{r}
tmpstereoL1_97D <- tmp %>% filter(slideid=="MULL_SUR_097_D")
tmpstereoL1_97D <-tmpstereoL1_97D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_97D <-tidyr::spread(tmpstereoL1_97D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_97D)
```

```{r}
kappam.fleiss(tmpstereoL1_97D)
```


### **5 - Slide MULL_SUR_104_G**

```{r plot9}
stereoL1_104G <- stereoL1 %>% filter(slideid == "MULL_SUR_104_G")

ggplot(data=stereoL1_104G, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_104G <- stereoL1_104G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test104G<-stereoL1_104G #%>% filter(diffperc > 3)
gt(test104G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 
Diff_104G <- as.data.frame(test104G$diffperc)
```


```{r}
tmpstereoL1_104G <- tmp %>% filter(slideid=="MULL_SUR_104_G")
tmpstereoL1_104G <-tmpstereoL1_104G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_104G <-tidyr::spread(tmpstereoL1_104G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_104G)
```

```{r}
kappam.fleiss(tmpstereoL1_104G)
```

### **6 - Slide MULL_SUR_107_D**

```{r plot10}
stereoL1_107D <- stereoL1 %>% filter(slideid == "MULL_SUR_107_D")

ggplot(data=stereoL1_107D, aes(x=factor(typecell, level = c("og","po1","po2", "cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_107D <- stereoL1_107D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test107D<-stereoL1_107D #%>% filter(diffperc > 3)
gt(test107D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  )
Diff_107D <- as.data.frame(test107D$diffperc)
```


```{r}
tmpstereoL1_107D <- tmp %>% filter(slideid=="MULL_SUR_107_D")
tmpstereoL1_107D <-tmpstereoL1_107D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_107D <-tidyr::spread(tmpstereoL1_107D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_107D)
```

```{r}
kappam.fleiss(tmpstereoL1_107D)
```


### **7 - Slide MULL_SUR_109_D**

```{r plot11}
stereoL1_109D <- stereoL1 %>% filter(slideid == "MULL_SUR_109_D")

ggplot(data=stereoL1_109D, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_109D <- stereoL1_109D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test109D<-stereoL1_109D #%>% filter(diffperc > 3)
gt(test109D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_109D <- as.data.frame(test109D$diffperc)
```


```{r}
tmpstereoL1_109D <- tmp %>% filter(slideid=="MULL_SUR_109_D")
tmpstereoL1_109D <-tmpstereoL1_109D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_109D <-tidyr::spread(tmpstereoL1_109D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_109D)
```

```{r}
kappam.fleiss(tmpstereoL1_109D)
```

### **8 - Slide MULL_SUR_115_G**

Plot 11 : Reading 1 by 2 agents

```{r}
stereoL1_115G <- stereoL1 %>% filter(slideid == "MULL_SUR_115_G")

ggplot(data=stereoL1_115G, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_115G <- stereoL1_115G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test115G<-stereoL1_115G #%>% filter(diffperc > 3)
gt(test115G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_115G <- as.data.frame(test115G$diffperc)
```


```{r}
tmpstereoL1_115G <- tmp %>% filter(slideid=="MULL_SUR_115_G")
tmpstereoL1_115G <-tmpstereoL1_115G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_115G <-tidyr::spread(tmpstereoL1_115G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_115G)
```

```{r}
kappam.fleiss(tmpstereoL1_115G)
```


### **9 - Slide MULL_SUR_134_D**

```{r plot13}
stereoL1_134D <- stereoL1 %>% filter(slideid == "MULL_SUR_134_D")

ggplot(data=stereoL1_134D, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_134D <- stereoL1_134D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test134D<-stereoL1_134D #%>% filter(diffperc > 3)
gt(test134D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  )

Diff_134D<- as.data.frame(test134D$diffperc)
```


```{r}
tmpstereoL1_134D <- tmp %>% filter(slideid=="MULL_SUR_134_D")
tmpstereoL1_134D <-tmpstereoL1_134D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_134D <-tidyr::spread(tmpstereoL1_134D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_134D)
```

```{r}
kappam.fleiss(tmpstereoL1_134D)
```


### **10 - Slide MULL_SUR_139_G**

```{r plot14}
stereoL1_139G <- stereoL1 %>% filter(slideid == "MULL_SUR_139_G")

ggplot(data=stereoL1_139G, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_139G <- stereoL1_139G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test139G<-stereoL1_139G #%>% filter(diffperc > 3)
gt(test139G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_139G<- as.data.frame(test139G$diffperc)
```


```{r}
tmpstereoL1_139G <- tmp %>% filter(slideid=="MULL_SUR_139_G")
tmpstereoL1_139G <-tmpstereoL1_139G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_139G <-tidyr::spread(tmpstereoL1_139G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_139G)
```

```{r}
kappam.fleiss(tmpstereoL1_139G)
```


### **11 - Slide MULL_SUR_245_D**

```{r plot15}
stereoL1_245D <- stereoL1 %>% filter(slideid == "MULL_SUR_245_D")

ggplot(data=stereoL1_245D, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_245D <- stereoL1_245D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test245D<-stereoL1_245D #%>% filter(diffperc > 3)
gt(test245D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 
Diff_245D<- as.data.frame(test245D$diffperc)
```


```{r}
tmpstereoL1_245D <- tmp %>% filter(slideid=="MULL_SUR_245_D")
tmpstereoL1_245D <-tmpstereoL1_245D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_245D <-tidyr::spread(tmpstereoL1_245D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_245D)
```

```{r}
kappam.fleiss(tmpstereoL1_245D)
```

### **12 - Slide MULL_SUR_248_G**

```{r plot16}
stereoL1_248G <- stereoL1 %>% filter(slideid == "MULL_SUR_248_G")

ggplot(data=stereoL1_248G, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_248G <- stereoL1_248G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test248G<-stereoL1_248G #%>% filter(diffperc > 3)
gt(test248G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_248G<- as.data.frame(test248G$diffperc)
```


```{r}
tmpstereoL1_248G <- tmp %>% filter(slideid=="MULL_SUR_248_G")
tmpstereoL1_248G <-tmpstereoL1_248G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_248G <-tidyr::spread(tmpstereoL1_248G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_248G)
```

```{r}
kappam.fleiss(tmpstereoL1_248G)
```

### **13 - Slide MULL_SUR_249_G**

```{r plot17}
stereoL1_249G <- stereoL1 %>% filter(slideid == "MULL_SUR_249_G")

ggplot(data=stereoL1_249G, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_249G <- stereoL1_249G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test249G<-stereoL1_249G #%>% filter(diffperc > 3)
gt(test249G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 
Diff_249G<- as.data.frame(test249G$diffperc)
```


```{r}
tmpstereoL1_249G <- tmp %>% filter(slideid=="MULL_SUR_249_G")
tmpstereoL1_249G <-tmpstereoL1_249G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_249G <-tidyr::spread(tmpstereoL1_249G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_249G)
```

```{r}
kappam.fleiss(tmpstereoL1_249G)
```


### **14 - Slide MULL_SUR_265_D**

```{r plot18}
stereoL1_265D <- stereoL1 %>% filter(slideid == "MULL_SUR_265_D")

ggplot(data=stereoL1_265D, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_265D <- stereoL1_265D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test265D <-stereoL1_265D #%>% filter(diffperc > 3)
gt(test265D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  )
Diff_265D<- as.data.frame(test265D$diffperc)
```


```{r}
tmpstereoL1_265D <- tmp %>% filter(slideid=="MULL_SUR_265_D")
tmpstereoL1_265D <-tmpstereoL1_265D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_265D <-tidyr::spread(tmpstereoL1_265D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_265D)
```

```{r}
kappam.fleiss(tmpstereoL1_265D)
```


### **15 - Slide MULL_SUR_270_G**

```{r plot19}
stereoL1_270G <- stereoL1 %>% filter(slideid == "MULL_SUR_270_G")

ggplot(data=stereoL1_270G, aes(x=factor(typecell, level = c("og","po1","po2","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL1_270G <- stereoL1_270G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test270G<-stereoL1_270G #%>% filter(diffperc > 3)
gt(test270G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_270G<- as.data.frame(test270G$diffperc)
```


```{r}
tmpstereoL1_270G <- tmp %>% filter(slideid=="MULL_SUR_270_G")
tmpstereoL1_270G <-tmpstereoL1_270G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL1_270G <-tidyr::spread(tmpstereoL1_270G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL1_270G)
```

```{r}
kappam.fleiss(tmpstereoL1_270G)
```
Summary of Diffperc for all structures on the 15 slides 

```{r data5}
typecell<- c('aoA','oaB','bv','cao','ct','E','gw','ho','Is','L','og','oih','po1','po2','POF','U','vtg')

Diff_total <- cbind(Diff_72D, Diff_91G, Diff_96D, Diff_97D, Diff_104G, Diff_107D, Diff_109D, Diff_115G, Diff_134D, Diff_139G, Diff_245D, Diff_248G, Diff_249G, Diff_265D, Diff_270G)

Tab_Diff_total_L1 <- cbind(typecell, Diff_total)
Tab_Diff_total_L1

```

## III - Second Reading

Set up the data list to get for the first reading 

```{r data6, results='hide'}
pathdata <-"C:/Users/csauger/Documents/These/Data/rouget/Lectures/Calibration/L2"
list1<-dir(paste0(pathdata,"/ALM"),patt="xml",full=T)
list2<-dir(paste0(pathdata,"/VM"),patt="xml",full=T)
list4<-dir(paste0(pathdata,"/CS"),patt="xml",full=T)
listcal<-c(list1,list2,list4)

```

Uploading the First Reading data from all 2 agents.

**readposition** is a function that will allow us to read the .xml files containing the stereology reading results of the agents, and extract information such as the agent that did the reading, the slide’s name ID, the structure’s name and their x and y coordonates. A loop is set up to import the .xml information, extracted with the readposition function, into a dataframe rezall.

```{r data7, results='hide'}

readposition<-function(nomfich){
xmlraw<-read_xml(listcal[idnom])
  nomnode<-xml_attr(xml_children(xmlraw),"Name")
  whichtypecell<-which(nomnode%in%c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","aoA","aoB","L","gw","ct","bv","Is","U","E"))
  rez<-data.frame()
  for(i in whichtypecell){
      typecell<-xml_attr(xml_children(xmlraw)[[i]],"Name")
      locpt<- xml_find_all(xml_children(xml_children(xmlraw)[[i]]),"Region")
      if(length(locpt)>0){
      xytmp<-data.frame()
      for(j in 1:length(locpt)){
          vertex<-xml_children(xml_children(locpt[[j]]))
          xtmp<-as.numeric(xml_attr(vertex,"X"))
          ytmp<-as.numeric(xml_attr(vertex,"Y"))
          xytmp<-rbind(xytmp,data.frame(idpt=j,x=xtmp,y=ytmp))
      }
      rez<-rbind(rez,data.frame(typecell=typecell,idpt=xytmp$idpt,x=xytmp$x,y=xytmp$y))
      }
  }
    rez<-rez%>%group_by(typecell,idpt)%>%summarise_all(median)%>%ungroup()%>%mutate(lame=listcal[idnom])
    agent<-sapply(strsplit(rez$lame,"/"),tail,2)
    rez$agent<-agent[1,]
    rez$slideid<-gsub(".xml","",agent[2,])
    rez<- rez%>%mutate(slideid=substr(slideid,1, nchar(slideid)-5))
    rez<-rez%>%select(-lame)
    return(rez)
}
rezallL2<-data.frame()
for(idnom in 1:length(listcal)){
  print(paste(idnom,listcal[idnom]))
  rez <- readposition(listcal[idnom])
  rez<-rez%>%group_by(slideid,x, y)%>%ungroup()
  rezallL2<-rbind(rez,rezallL2)
}

```
Checking if every agent has the same number of sampling points read

```{r , message=FALSE}
countcheck <- rezallL2 %>% group_by(slideid, agent) %>% summarise(total_points= n())
countcheck <- countcheck %>% spread(key = "agent", value = total_points)
countcheck
```

Set up of the main dataframe
We add the same color codes (colormat), used during the stereology reading, to the reading results dataframe (tmp).

```{r , results='hide'}
tmp <- rezallL2 %>% unite("id", x:y, remove = FALSE)
tmp <- tmp %>% mutate(reading = "1")
colormat<-data.frame(typecell= c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","aoA","aoB","L","gw","ct","bv","Is","U","E"), matcolor =  c("lightgoldenrod1","yellow","orange","red","gray0","lightpink1","deeppink2","darkslategray1","cyan3","gray52","gray88","thistle1","darkgreen","seagreen1","firebrick1","cornflowerblue","mediumpurple3","white"), stringsAsFactors = F)
tmp <-left_join(tmp,colormat,by="typecell")
```

We re-organize the dataframe, adding the total number of points counted for each slide (total_points), the agent that did the reading, the name of the slide (slideid) and the percentage count of each structure (fract_estim).

The 18 cellular structures that can be found are :

-**og**: oogonium  
-**po1**: primary oocyte stage 1  
-**po2**: primary oocyte stage 2 
-**ldo**: lipid droplet oocyte
-**cao**: cortical alveoli oocyte  
-**vtg**: oocyte in vitellogenesis  
-**oih**: oocyte in hydration  
-**oh**: hydrated oocyte  
-**POF**: post-Ovulatory Follicle  
-**aoA**: atretic oocyte alpha  
-**aoB**: atretic oocyte beta  
-**L**: lysis  
-**bv**: blood vessel  
-**Is**: intercellular space  
-**gw**: gonadal wall  
-**ct**: connective tissue  
-**E**: unatural emptiness  
-**U**: undetermined  


```{r , results='hide',message=FALSE}
histo2 <- rezallL2 %>% group_by(typecell, slideid, agent) %>% summarise(hit_points= n())
histo3 <- histo2 %>% spread(key = "typecell", value = hit_points) 
histo3[is.na(histo3)] <- 0
histo4 <- (histo3[,3:20]*100)/(rowSums(histo3[,3:20]))#check number of columns histo3
histo5 <- cbind(histo4, histo3$slideid) %>% rename(slideid = `histo3$slideid`)
histo6 <- rezallL2 %>% group_by(slideid, agent) %>% summarise(total_points= n())
histo5 <- cbind(histo5, histo6$total_points) %>% rename(total_points = `histo6$total_points`)
histo5 <- cbind(histo5, histo6$agent) %>% rename(agent = `histo6$agent`)

stereoL2 <- gather(histo5, key = "typecell", value = fract_estim, aoA,aoB,bv,cao,ct,E,gw,ho,Is,L,ldo,og,oih,po1,po2,POF,U,vtg)

```

Plot 4: Results of the first reading exercise, for 15 slides by 2 agents

```{r plot20, fig.height=10,fig.width=15}
hist_tot_dif <- ggplot(data=stereoL2, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent : ")
hist_tot_dif
#ggsave(hist_tot_dif, file = "C:/Users/vmartin/Desktop/Stage/pour_erreur/hist_tot_dif.png")
```

Comparing the reading results for all 15 slides

Statistics on the counted surface values found by 4 readers

-minsurf % : minimum value, for the counted cellular structure (%), found between the 3 reading agents  
-maxsurf % : maximum value, for the counted cellular structure (%), found between the 3 reading agents  
-diffperc % : diffrence between the min (minsurf) and the max (maxsurf) values  
-sdperc % : standard deviation for the min and max values found between the reading agents  
-meanperc % : mean of the min and max values found between the reading agents  
-CV % : Coefficient of Variation, no unit, expressed in %.  
-medianeperc % : median value (%) of the counted cellular structures  
-madperc % : Mean Absolute Deviation of the counted cellular structures (%).  

### **1 - Slide MULL_SUR_072_D**

```{r plot21}
stereoL2_72D <- stereoL2 %>% filter(slideid == "MULL_SUR_072_D")

ggplot(data=stereoL2_72D, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_72D <- stereoL2_72D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test72D<-stereoL2_72D #%>% filter(diffperc > 3)
gt(test72D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  )

Diff_72D <- as.data.frame(test72D$diffperc)
```

```{r}
tmpstereoL2_72D <- tmp %>% filter(slideid=="MULL_SUR_072_D")
tmpstereoL2_72D <-tmpstereoL2_72D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_72D <-tidyr::spread(tmpstereoL2_72D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_72D)
```

```{r}
kappam.fleiss(tmpstereoL2_72D)
```

### **2 - MULL_SUR_091_G**

```{r plot22}
stereoL2_91G <- stereoL2 %>% filter(slideid == "MULL_SUR_091_G")

ggplot(data=stereoL2_91G, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_91G <- stereoL2_91G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test91G<-stereoL2_91G #%>% filter(diffperc > 3)
gt(test91G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 
Diff_91G <- as.data.frame(test91G$diffperc)
```


```{r}
tmpstereoL2_91G  <- tmp %>% filter(slideid=="MULL_SUR_091_G")
tmpstereoL2_91G  <-tmpstereoL2_91G %>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_91G  <-tidyr::spread(tmpstereoL2_91G ,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_91G )
```

```{r}
kappam.fleiss(tmpstereoL2_91G)
```

### **3 - Slide MULL_SUR_096_D**

```{r plot23}
stereoL2_96D <- stereoL2 %>% filter(slideid == "MULL_SUR_096_D")

ggplot(data=stereoL2_96D, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_96D <- stereoL2_96D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test96D<-stereoL2_96D #%>% filter(diffperc > 3)
gt(test96D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_96D <- as.data.frame(test96D$diffperc)
```


```{r}
tmpstereoL2_96D <- tmp %>% filter(slideid=="MULL_SUR_096_D")
tmpstereoL2_96D <-tmpstereoL2_96D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_96D <-tidyr::spread(tmpstereoL2_96D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_96D)
```

```{r}
kappam.fleiss(tmpstereoL2_96D)
```


### **4 - Slide MULL_SUR_097_D**

```{r plot24}
stereoL2_97D <- stereoL2 %>% filter(slideid == "MULL_SUR_097_D")

ggplot(data=stereoL2_97D, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_97D <- stereoL2_97D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test97D<-stereoL2_97D #%>% filter(diffperc > 3)
gt(test97D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_97D <- as.data.frame(test97D$diffperc)
```


```{r}
tmpstereoL2_97D <- tmp %>% filter(slideid=="MULL_SUR_097_D")
tmpstereoL2_97D <-tmpstereoL2_97D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_97D <-tidyr::spread(tmpstereoL2_97D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_97D)
```

```{r}
kappam.fleiss(tmpstereoL2_97D)
```


### **5 - Slide MULL_SUR_104_G**

```{r plot25}
stereoL2_104G <- stereoL2 %>% filter(slideid == "MULL_SUR_104_G")

ggplot(data=stereoL2_104G, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_104G <- stereoL2_104G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test104G<-stereoL2_104G #%>% filter(diffperc > 3)
gt(test104G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 
Diff_104G <- as.data.frame(test104G$diffperc)
```


```{r}
tmpstereoL2_104G <- tmp %>% filter(slideid=="MULL_SUR_104_G")
tmpstereoL2_104G <-tmpstereoL2_104G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_104G <-tidyr::spread(tmpstereoL2_104G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_104G)
```

```{r}
kappam.fleiss(tmpstereoL2_104G)
```

### **6 - Slide MULL_SUR_107_D**

```{r plot26}
stereoL2_107D <- stereoL2 %>% filter(slideid == "MULL_SUR_107_D")

ggplot(data=stereoL2_107D, aes(x=factor(typecell, level = c("og","po1","po2", "cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_107D <- stereoL2_107D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test107D<-stereoL2_107D #%>% filter(diffperc > 3)
gt(test107D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  )
Diff_107D <- as.data.frame(test107D$diffperc)
```


```{r}
tmpstereoL2_107D <- tmp %>% filter(slideid=="MULL_SUR_107_D")
tmpstereoL2_107D <-tmpstereoL2_107D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_107D <-tidyr::spread(tmpstereoL2_107D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_107D)
```

```{r}
kappam.fleiss(tmpstereoL2_107D)
```


### **7 - Slide MULL_SUR_109_D**

```{r plot27}
stereoL2_109D <- stereoL2 %>% filter(slideid == "MULL_SUR_109_D")

ggplot(data=stereoL2_109D, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_109D <- stereoL2_109D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test109D<-stereoL2_109D #%>% filter(diffperc > 3)
gt(test109D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_109D <- as.data.frame(test109D$diffperc)
```


```{r}
tmpstereoL2_109D <- tmp %>% filter(slideid=="MULL_SUR_109_D")
tmpstereoL2_109D <-tmpstereoL2_109D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_109D <-tidyr::spread(tmpstereoL2_109D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_109D)
```

```{r}
kappam.fleiss(tmpstereoL2_109D)
```

### **8 - Slide MULL_SUR_115_G**

Plot 11 : Reading 1 by 2 agents

```{r}
stereoL2_115G <- stereoL2 %>% filter(slideid == "MULL_SUR_115_G")

ggplot(data=stereoL2_115G, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_115G <- stereoL2_115G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test115G<-stereoL2_115G #%>% filter(diffperc > 3)
gt(test115G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_115G <- as.data.frame(test115G$diffperc)
```


```{r}
tmpstereoL2_115G <- tmp %>% filter(slideid=="MULL_SUR_115_G")
tmpstereoL2_115G <-tmpstereoL2_115G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_115G <-tidyr::spread(tmpstereoL2_115G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_115G)
```

```{r}
kappam.fleiss(tmpstereoL2_115G)
```


### **9 - Slide MULL_SUR_134_D**

```{r plot28}
stereoL2_134D <- stereoL2 %>% filter(slideid == "MULL_SUR_134_D")

ggplot(data=stereoL2_134D, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_134D <- stereoL2_134D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test134D<-stereoL2_134D #%>% filter(diffperc > 3)
gt(test134D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  )

Diff_134D<- as.data.frame(test134D$diffperc)
```


```{r}
tmpstereoL2_134D <- tmp %>% filter(slideid=="MULL_SUR_134_D")
tmpstereoL2_134D <-tmpstereoL2_134D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_134D <-tidyr::spread(tmpstereoL2_134D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_134D)
```

```{r}
kappam.fleiss(tmpstereoL2_134D)
```


### **10 - Slide MULL_SUR_139_G**

```{r plot29}
stereoL2_139G <- stereoL2 %>% filter(slideid == "MULL_SUR_139_G")

ggplot(data=stereoL2_139G, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_139G <- stereoL2_139G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test139G<-stereoL2_139G #%>% filter(diffperc > 3)
gt(test139G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_139G<- as.data.frame(test139G$diffperc)
```


```{r}
tmpstereoL2_139G <- tmp %>% filter(slideid=="MULL_SUR_139_G")
tmpstereoL2_139G <-tmpstereoL2_139G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_139G <-tidyr::spread(tmpstereoL2_139G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_139G)
```

```{r}
kappam.fleiss(tmpstereoL2_139G)
```


### **11 - Slide MULL_SUR_245_D**

```{r plot30}
stereoL2_245D <- stereoL2 %>% filter(slideid == "MULL_SUR_245_D")

ggplot(data=stereoL2_245D, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_245D <- stereoL2_245D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test245D<-stereoL2_245D #%>% filter(diffperc > 3)
gt(test245D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 
Diff_245D<- as.data.frame(test245D$diffperc)
```


```{r}
tmpstereoL2_245D <- tmp %>% filter(slideid=="MULL_SUR_245_D")
tmpstereoL2_245D <-tmpstereoL2_245D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_245D <-tidyr::spread(tmpstereoL2_245D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_245D)
```

```{r}
kappam.fleiss(tmpstereoL2_245D)
```

### **12 - Slide MULL_SUR_248_G**

```{r plot31}
stereoL2_248G <- stereoL2 %>% filter(slideid == "MULL_SUR_248_G")

ggplot(data=stereoL2_248G, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_248G <- stereoL2_248G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test248G<-stereoL2_248G #%>% filter(diffperc > 3)
gt(test248G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_248G<- as.data.frame(test248G$diffperc)
```


```{r}
tmpstereoL2_248G <- tmp %>% filter(slideid=="MULL_SUR_248_G")
tmpstereoL2_248G <-tmpstereoL2_248G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_248G <-tidyr::spread(tmpstereoL2_248G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_248G)
```

```{r}
kappam.fleiss(tmpstereoL2_248G)
```

### **13 - Slide MULL_SUR_249_G**

```{r plot32}
stereoL2_249G <- stereoL2 %>% filter(slideid == "MULL_SUR_249_G")

ggplot(data=stereoL2_249G, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_249G <- stereoL2_249G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test249G<-stereoL2_249G #%>% filter(diffperc > 3)
gt(test249G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 
Diff_249G<- as.data.frame(test249G$diffperc)
```


```{r}
tmpstereoL2_249G <- tmp %>% filter(slideid=="MULL_SUR_249_G")
tmpstereoL2_249G <-tmpstereoL2_249G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_249G <-tidyr::spread(tmpstereoL2_249G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_249G)
```

```{r}
kappam.fleiss(tmpstereoL2_249G)
```


### **14 - Slide MULL_SUR_265_D**

```{r plot33}
stereoL2_265D <- stereoL2 %>% filter(slideid == "MULL_SUR_265_D")

ggplot(data=stereoL2_265D, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_265D <- stereoL2_265D %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test265D <-stereoL2_265D #%>% filter(diffperc > 3)
gt(test265D)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  )
Diff_265D<- as.data.frame(test265D$diffperc)
```


```{r}
tmpstereoL2_265D <- tmp %>% filter(slideid=="MULL_SUR_265_D")
tmpstereoL2_265D <-tmpstereoL2_265D%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_265D <-tidyr::spread(tmpstereoL2_265D,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_265D)
```

```{r}
kappam.fleiss(tmpstereoL2_265D)
```


### **15 - Slide MULL_SUR_270_G**

```{r plot34}
stereoL2_270G <- stereoL2 %>% filter(slideid == "MULL_SUR_270_G")

ggplot(data=stereoL2_270G, aes(x=factor(typecell, level = c("og","po1","po2","ldo","cao","vtg","oih","ho","POF","L","aoA","aoB","gw","ct","bv","Is","U","E")), y=fract_estim, fill=agent)) +
  geom_bar(stat = "identity",  position=position_dodge()) +
  xlab("Cellular structures") +
  facet_wrap(~slideid)+
  ylab("Structure count") +
  theme(axis.text.x = element_text(size=9, angle = 90)) +
  scale_fill_discrete(name="Agent")
```

To validate a reading: need to have a difference of less than 3% between the highest and lowest values, for a single cellular structure inside a single slide

```{r}
stereoL2_270G <- stereoL2_270G %>% group_by(typecell)%>%
  summarise(minsurf= min(fract_estim,na.rm=T),
           maxsurf= max(fract_estim,na.rm=T),
           diffperc=maxsurf-minsurf,
           sdperc=sd(fract_estim,na.rm=T),
           meanperc=mean(fract_estim,na.rm=T),
           CV=sdperc/meanperc*100,
           medianperc=median(fract_estim,na.rm=T),
           madperc=mad(fract_estim,na.rm=T))

test270G<-stereoL2_270G #%>% filter(diffperc > 3)
gt(test270G)%>% 
  tab_style(
    style = list(
      cell_text(color = "red", style = "italic")
    ),
    locations = cells_body(
      columns = 4
    )
  ) 

Diff_270G<- as.data.frame(test270G$diffperc)
```


```{r}
tmpstereoL2_270G <- tmp %>% filter(slideid=="MULL_SUR_270_G")
tmpstereoL2_270G <-tmpstereoL2_270G%>% group_by(id,slideid,agent)%>%dplyr::summarise(typecell=first(typecell))%>%ungroup()
tmpstereoL2_270G <-tidyr::spread(tmpstereoL2_270G,agent,typecell)%>%select(-id,-slideid)

agree(tmpstereoL2_270G)
```

```{r}
kappam.fleiss(tmpstereoL2_270G)
```
Summary of Diffperc for all structures on the 15 slides 

```{r data8}
typecell<- c('aoA','oaB','bv','ldo','cao','ct','E','gw','ho','Is','L','og','oih','po1','po2','POF','U','vtg')

Diff_total <- cbind(Diff_72D, Diff_91G, Diff_96D, Diff_97D, Diff_104G, Diff_107D, Diff_109D, Diff_115G, Diff_134D, Diff_139G, Diff_245D, Diff_248G, Diff_249G, Diff_265D, Diff_270G)

Tab_Diff_total_L2 <- cbind(typecell, Diff_total)
Tab_Diff_total_L2

```

